---
title: "Restaurant Scores - LIVES Standard"
author: "Amal Almutairy"
date: "11-10-2020"
output:
  html_document:
    theme: journal
    highlight: tango
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: no
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
```

## Health And Social Services
After conducting an inspection of the facility, the Health Inspector calculates a score based on the violations observed.The score card data is avilible to the puplic in Health And Social Services websit: `https://data.sfgov.org/Health-and-Social-Services/Restaurant-Scores-LIVES-Standard/pyih-qa8i?row_index=0`



```{r}
# Packages required
library(rsample)
library(caret)
library(tidyverse)
library(readr)
library(ggplot2)
library(dplyr)
library(recipes)
library(ggvis)
library(vip) 
```

## Restaurant Scores - LIVES Standard
```{r}
# Read the data:
library(readr)
Rscore <- read_csv("Restaurant_Scores_-_LIVES_Standard.csv", 
    col_types = cols(business_id = col_number(), 
        violation_id = col_number()))
View(Rscore)
Rscore = na.omit(Rscore)
```

# Exploratory Data Analysis
```{r}
# EDA
str(Rscore)
summary(Rscore)
class(Rscore)
head(Rscore)
glimpse(Rscore)
```

# Inspection Score Density Spread
```{r}
summary(Rscore$inspection_score)


# Plot
hist(Rscore$inspection_score)
plot(density(Rscore$inspection_score), main="Inspection Score Density Spread")
```
# Risk Category Rates 
```{r}
summary(Rscore$risk_category)

# Plot
ggplot(Rscore, aes(x = risk_category)) +
  theme_bw() +
  geom_bar() +
  labs(y = "Violations count",
       title = "Risk Category Rates")

```

```{r}
# split, train and test the data 
set.seed(123) # for reproducibility
split <- initial_split(Rscore, strata = "inspection_score", prop = 0.7)
train <- training(split)
test  <- testing(split) 


# Do the distributions line up? 
ggplot(train, aes(x = inspection_score)) + 
  geom_line(stat = "density", 
            trim = TRUE) + 
  geom_line(data = test, 
            stat = "density", 
            trim = TRUE, col = "red")
```
## Feature engineering
```{r}
visdat::vis_miss(Rscore, cluster = TRUE)

caret::nearZeroVar(Rscore, saveMetrics= TRUE) %>% 
  rownames_to_column() %>% 
  filter(nzv)
```


```{r}

# 1. stratified sampling with the rsample package
set.seed(1234)
split  <- initial_split(Rscore, prop = 0.7, strata = "inspection_score")
rtrain  <- training(split)
rtest   <- testing(split)

# 2. Feature engineering
blueprint <- recipe(inspection_score ~ business_id, data = Rscore) %>%
  step_nzv(all_nominal()) %>%
  step_integer(matches("Qual|Cond|QC|Qu")) %>%
  step_center(all_numeric(), -all_outcomes()) %>%
  step_scale(all_numeric(), -all_outcomes()) %>%
  step_dummy(all_nominal(), -all_outcomes(), one_hot = TRUE)

# prepare blueprint
prepare <- prep(blueprint, training = Rscore)
prepare

# Bake
baked_train <- bake(prepare, new_data = Rscore)
baked_test <- bake(prepare, new_data = Rscore)

baked_train
```


```{r}

# 3. create a re-sampling method
cv <- trainControl(
  method = "repeatedcv", 
  number = 10, 
  repeats = 5
  )
 
# 4. create a hyperparameter grid search
hyper_grid <- expand.grid(k = seq(2, 25, by = 1))

# 5. execute grid search with knn model
#    use RMSE as preferred metric
knn_fit <- train(
  blueprint, 
  data = rtrain, 
  method = "knn", 
  trControl = cv, 
  tuneGrid = hyper_grid,
  metric = "RMSE"
  )
# 6. evaluate results
# print model results
knn_fit
```


```{r}
# 
ggplot(Rscore, aes(x = inspection_score)) +
  theme_bw() +  
  facet_wrap(~ risk_category) +
  geom_bar() +
  labs(y = "Violations count",
       title = "Risk Category Rates by Inspection Score")
```
```{r}
# plot cross validation results
ggplot(knn_fit$results, aes(k, RMSE)) + 
  geom_line() +
  geom_point() +
  scale_y_continuous(labels = scales::dollar)  
```